---
title: "Coursera_Developing data product(week3)"
author: "Taesoon Kim"
output:
  beamer_presentation: default
  ioslides_presentation: default
Date: Jul-21-2017
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction & Goal
  - This project is the part of coursera lecture, developing data product.
  
  - The goal of this project is to create a web page presentation using R markdown that features a plot created with Plotly.
  
  - I will draw a graph using plotly() function, and make a web page presentation.
  
  - Download the KOSPI(Korean Composite Stock Price Index) figures and using plot_ly() function, I will draw a graph


## Set the route and load library
```{r set}
setwd("D:/1-1. R studio/Lecture9. Developing data product/week3")

# Today date
format(Sys.Date(),"%m-%d-%Y")
```

```{r load,include=FALSE}
# install.packages("plotly")
library(plotly)
```

  - Load the library and check today's date.
  - Today is Jul-21-2017

## Read file and Process data

```{r draw}
# Read csv file
library(data.table)
stock_data<-fread("kospi.csv",sep=",",header=TRUE)

# Sort the file order by date
library(lubridate)
stock_data$Date <- dmy(stock_data$Date)
stock_order<-stock_data[order(Date),]

# Calculate mean stock  of each day 
stock_order$Avg<-1:nrow(stock_order)
stock_order$Avg<-rowMeans(data.frame(stock_order$High,stock_order$Low))
```

## Plot the result
```{r plot, echo=FALSE}
# Plot
library(ggplot2)
plot_ly(stock_order,x=~Date,y=~Avg,mode="markers")%>%
  layout(title="KOSPI figures from 2003 ~ 2017",xaxis=list(title="Year"),yaxis=list(title="Stock Figure")) %>%
  add_ribbons(ymin=~Low,ymax=~High,name="Range of day") %>%
  add_lines(color=I("red"),name="Average of day")
```


